\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
fix(paper): fixed formatting in references so outputted pdf citations work, + small grammatical fix

\subsection{ByteBuddy}
ByteBuddy is a popular code generation and manipulation library for creating and modifying Java classes during the runtime of a Java application\cite{bytebuddy}. The bytebuddy library allows a user can inject classes into a running JVM dynamically. Since it is a Java library, it is easier and more intuitive than Byteman rules. However, we do believe that the simplicity of Byteman rules are perferred compared to learning a new library.

@@

\bibitem{aspectj}
Introduction to aspectj
\\\texttt{https://www.eclipse.org/aspectj/doc/released/progguide/starting-aspectj.html}

>>>>

\subsection{ByteBuddy}
ByteBuddy is a popular code generation and manipulation library for creating and modifying Java classes during the runtime of a Java application\cite{bytebuddy}. The bytebuddy library allows a user to inject classes into a running JVM dynamically. Since it is a Java library, it is easier and more intuitive than Byteman rules. However, we do believe that the simplicity of Byteman rules are perferred compared to learning a new library.

@@

\bibitem{aspectj}
Introduction to aspectj
\\\texttt{https://www.eclipse.org/aspectj/doc/\newline released/progguide/starting-aspectj.html}
